Reply To Examiners

### 2014-05-21 answer_thesis_examiner/chap1.tex
Ian's changes

First, I would like to express my appreciation towards Examiner No. 1 for his \textbf{over-all positive comments}.
I also appreciate the fact that Examiner No 1 includes
  not only his comments in the examiner's report
  but also helpful suggestions inside the original thesis.
There was no direct question in the report, and followings are my replies to his comments in the returned thesis.

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
\endhead
4 & 5 & missing references & citation added \\
4 & 8 & missing references & citation added \\
5 & 13 & techniques ... has & techniques ... have \\
6 & 5 & many fold & manyfold \\
14 & 5 & Assuming the number of these elementary back scatterers is sufficiently large, & Assuming these elementary back scatterers are large in numbers and independent in nature, \\
14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\
\end{longtable}    
\rowcolors{1}{white}{}

@@

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections \& Comments} \\
 \hline
 \endhead
15 & 6 & missing explaination for $\vec{E},B$ & explaination added \\
15 & 12 & x,y plane & x \& y planes \\
15 & -2 & $2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi)$ & $2 \frac{\xi_x(t) \xi_y(t)}{E_x^0 E_y^0} \cos (\Delta \phi)$ \\
16 & 2 & The parameters ... are: & The parameters ... are: the intensity orientation angle ($\theta$), the ellipticity angle ($\Psi$) and the orientation angle ($\chi$) \\
17 & 4 & machenics & mechanics \\
17 & -1 & missing explaination for $\Re,\Im$ & explaination added \\
20 & -1 & font size for Eqns 2.10 and 2.11 is different from the rest of the thesis & This is due to space restriction, where the matrix representation in the normal font size would require a larger width that that is available in one line \\
33 & -10 & Eqn. [2.15) & Eqn. 2.15 \\
34 & 10 & how did you get this Eqn? & References are added for each Equation \\
35 & 10 & which distribution is more appropriate & The most appropriate distribution is the distribution of the ``true signal'', which of course, is unknown \\
43 & -3 & $pdf(A_1)=2A_1e^{A_1^2}$ & $pdf(A_1)=2A_1e^{-A_1^2}$ \\
76 & -4 & chapter 2 & Chapter 2 \\
129 & 1 & cahpter 5 & Chapter 5 \\
129 & 6 & theoretical results & theoretical contributions \\
129 & 21 & this thesis unite & this thesis unites \\
130 & 1 & articles that has been & articles that have been \\
132 & 14 & an important benefits & several important benefits \\
\end{longtable}    
\rowcolors{1}{white}{}

>>>>

First, I would like to express my appreciation towards Examiner No. 1 for his \textbf{over-all positive comments}.
I also appreciate the fact that Examiner No 1 includes
  not only his comments in the examiner's report
  but also helpful suggestions inside the original thesis.

The examiner asked no direct question in his comments, so the following are my replies to his comments as listed in the returned thesis:

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
\endhead
4 & 5 & missing references & citation added \\
4 & 8 & missing references & citation added \\
5 & 13 & techniques ... has & techniques ... have \\
6 & 5 & many fold & manyfold \\
14 & 5 & Assuming the number of these elementary back scatterers is sufficiently large, & Assuming these elementary back scatterers are large in number and independent in nature, \\
%**IVM: the above should be 'number' (you had written 'numbers')
14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\
%**IVM: did you mention this in the thesis? If so, it might be good to mention.
\end{longtable}    
\rowcolors{1}{white}{}

@@

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections \& Comments} \\
 \hline
 \endhead
15 & 6 & missing explaination for $\vec{E},B$ & explaination added \\
15 & 12 & x,y plane & x \& y planes \\
15 & -2 & $2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi)$ & $2 \frac{\xi_x(t) \xi_y(t)}{E_x^0 E_y^0} \cos (\Delta \phi)$ \\
16 & 2 & The parameters ... are: & The parameters ... are: the intensity orientation angle ($\theta$), the ellipticity angle ($\Psi$) and the orientation angle ($\chi$) \\
17 & 4 & machenics & mechanics \\
17 & -1 & missing explaination for $\Re,\Im$ & explaination added \\
20 & -1 & font size for Eqns 2.10 and 2.11 is different from the rest of the thesis & This is due to space restriction, where the matrix representation in the normal font size would require a larger width that that is available in one line \\
33 & -10 & Eqn. [2.15) & Eqn. 2.15 \\
34 & 10 & how did you get this Eqn? & References have now been added to show the source of the equation \\
35 & 10 & which distribution is more appropriate & The most appropriate distribution is that of the ``true signal'', which of course, is unknown, so we are trying to model it \\
43 & -3 & $pdf(A_1)=2A_1e^{A_1^2}$ & $pdf(A_1)=2A_1e^{-A_1^2}$ \\
76 & -4 & chapter 2 & Chapter 2 \\
129 & 1 & cahpter 5 & Chapter 5 \\
129 & 6 & theoretical results & theoretical contributions \\
129 & 21 & this thesis unite & this thesis unites \\
130 & 1 & articles that has been & articles that have been \\
132 & 14 & an important benefits & several important benefits \\
\end{longtable}    
\rowcolors{1}{white}{}

### 2014-05-21 answer_thesis_examiner/chap2.tex
Ian's changes

\replyToComment
    {Sec 1.1 and 1.2 should be reviewed again ... with proper citations on the background studies.}
    {The sections were reviewed and several citations were added}

\replyToComment
    {Paragraph 1 of Sec 1.3.3 should be removed or rewritten}
    {The paragraph were removed?}

\replyToComment
    {The achievement of objectives should (also) be stated in the conclusion chapter. }
    {These were added into the conclusion chapter (``with proper justfications based on experimental results and findings'').}

\replyToComment
    {Replace the word ``theory'' with ``model'' throughout the thesis}
    {Search and replace operation done!}

\replyToComment
    {The proposed model is derived based on the existing statistical models for SAR and extended to POLSAR}
    {The main approach, as described in the thesis, differs in a subtle but important way.
The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
That is: the proposed models by nature are applicable to multi-dimensional data and thus they are applicable to POLSAR data.
To show that the proposed models are also applicable to SAR data, the dimension parameters in these models are collapsed into 1.
The thesis subsequently shows that they match perfectly with existing SAR models.
}

\replyToComment
    {The proposed log-transform model will introduce an inevitable bias error, which may not be able to measure by MSE.}
    {
      The thesis clearly recognizes that log-transformation will introduce bias.
      It also shows that MSE evaluation does inherently include bias evaluation.
      In fact, the thesis argues that MSE evaluation has two components: 1. bias evaluation and 2. variance evaluation, which for evaluating the performance of SAR speckle filters translates into 1. radiometric preservation and 2. noise suppression respectively.
}

\replyToComment
    {A more comprehensive review of the relevant SAR/POLSAR speckle filters should be included.}
    {The most recent review \cite{Argenti_GRSM_2013} has been included together with several other publications \cite{Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}}

\replyToComment
    {Whereever possible, samples of SAR/POLSAR images with these three types of features (i.e. homogeneous, textured and strong scatterer) should be used to evaluate the effectiveness of the proposed models.}
    {In the section to evaluate speckle filters, various different patterns had been studied. Also the MSE evaluation which includes bias and variance evaluation are shown to be able to evaluate the effectiveness of different speckle filters in terms of radiometric preservation and speckle noise reduction respectively.}

\replyToComment
    {The work done has great potential to be published in high impact factor journals such as JSTAR, IJRS and PIER}
    {I appreciate the Examiner's vote of confidence. Portions of the thesis has been extracted out as academic papers and submitted for peer-review.}

\replyToComment
    {Define terms heteroskedastic and homoskedastic in the context of SAR imagery.}
    {Heteroskedastic and homoskedastic are terms defined in statistical context to respectively denote the fact that different sub-populations of a given samples can have different or similar variabilities. In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or the same variances.}

@@

\replyToComment
    {Add references to the following statement: ``most of these data processing techniques are traditionally designed for additive and homoskedastic data.''}
    {Reference added: most of these data processing techniques are traditionally designed for additive and homoskedastic data \cite{Dutch_LNCS_2004}.}

@@

\replyToComment
    {It would be easier to read and refer if all the Equations are labelled accordingly.}
    {All equations in the thesis has been updated with labels.}

@@

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
3 & 12 & Similarly speaking, & Similarly, \\
3 & 19 & criteria & criterion \\ 
4 & 14 & MMSE criteria & MMSE criterion \\
6 & 9 & Last but certainly not least, & Thirdly, \\ 
6 & 9 & such a framework allow & such a framework allows \\
9 & 7 & multidimensional & Multi-dimensional \\
10 & 12 & The model os & The model is \\
11 & 28 & chapter 5 & Chapter 5 \\
12 & 6 & chapter 6 & Chapter 6 \\
22 & 15 & RadarSat & RadarSat-2 \\
24 & 14 & SVM & SVM (Support Vector Machine) \\
35 & 6-7 & Rician distribution [48]... & Rician distribution [48]. \\
35 & 11 & back scattering & backscattering \\
36 & 10 & literatured & literatures \\
37 & -2 & Proposed bu & proposed by \\
39 & 4 & dependence & dependency \\
44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence is rephrased \\
46 & 4 & most known common & most commonly known \\
56 & 6 & POLSAR And & POLSAR. And \\
65 &5,7 & an homogeneous area & a homogeneous area \\
77 & 3 & the objective then is & the objective is \\
77 & 5,6 & it has already been proven & it has already been proven [?] \\
87 & -1 & Fig 5.6a & Fig 5.6. \\
89 & - & Figure 5.6 - subtitle (a) & (a) is removed \\
91 & - & Figure 5.8: Legends are too small to read & They are enlarged \\
95 & - & Figure 5.12 & Use the same scale for  y axis (i.e MSE 0:1) across all the plots \\
103 & 22 & related to the ENL index. over & related to the ENL index over \\
104 & 13 & Equation 5.3.2.1 & The number is corrected to (?) \\
109 & 8 & Figs. 5.21c and 5.21d allows & Fig 5.21(a) and Fig 5.21(d) allow \\
112 & 13 & these smaller requirements & these requirements \\
132 & 9 & evaluation criteria & evaluation criterion
\end{longtable}    
\rowcolors{1}{white}{}

@@

In general, I wish to express my appreciation towards Examiner No. 2 for his careful, detailed and concise review.
I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
I also feel encouraged by the Examiner's suggestion to extract out portions of this thesis as scientific papers for peer review, which has also been taken up and acted upon.

>>>>

I would like to thank Examiner 2 for examining the thesis carefully. I have listed the comments below, and responded to each one. I have also rectified all of the items in the errata.

\replyToComment
    {Sec 1.1 and 1.2 should be reviewed again ... with proper citations on the background studies.}
    {This has been done: both sections have been reviewed with several new citations added}

\replyToComment
    {Paragraph 1 of Sec 1.3.3 should be removed or rewritten}
    {The paragraph were removed?}
%**IVM: why the question mark??
\replyToComment
    {The achievement of objectives should (also) be stated in the conclusion chapter. }
    {These have now been added into the conclusion chapter (with proper justfications based on experimental results and findings).}

\replyToComment
    {Replace the word ``theory'' with ``model'' throughout the thesis}
    {This has been done.}
%**IVM better not use humour... not all examiners have a sense of humour!!    {Search and replace operation done!}

\replyToComment
    {The proposed model is derived based on the existing statistical models for SAR and extended to POLSAR}
    {The main approach, as described in the thesis, differs in a subtle but important way.
The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
That is: the proposed models by nature are applicable to multi-dimensional data and thus to POLSAR data.
To show that the proposed (multidimensional) models are also applicable to SAR data, the dimension parameters in these models are collapsed into 1. The thesis subsequently shows that they match perfectly with existing SAR models.
}

\replyToComment
    {The proposed log-transform model will introduce an inevitable bias error, which may not be able to measure by MSE.}
    {
      It is true. In fact, the thesis does say that log-transformation will introduce bias. %**IVM
      It also shows that MSE evaluation does inherently include a bias evaluation.
      In fact, the thesis argues that MSE evaluation has two components: 1. bias evaluation and 2. variance evaluation, which, for evaluating the performance of SAR speckle filters translates into two criteria: 1. radiometric preservation and 2. noise suppression respectively.
}

\replyToComment
    {A more comprehensive review of the relevant SAR/POLSAR speckle filters should be included.}
    {The most recent review \cite{Argenti_GRSM_2013} has been included together with several other publications \cite{Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}, all discussed within the thesis.}

\replyToComment
    {Wherever possible, samples of SAR/POLSAR images with these three types of features (i.e. homogeneous, textured and strong scatterer) should be used to evaluate the effectiveness of the proposed models.}
    {In the section on evaluating speckle filters, various different patterns have been studied. Also the MSE evaluation which includes bias and variance evaluation are shown to be able to evaluate the effectiveness of different speckle filters in terms of radiometric preservation and speckle noise reduction respectively.}
%**IVM: Hai - do you think that this answers the examiners question? Maybe he is looking for visual examples?

\replyToComment
    {The work done has great potential to be published in high impact factor journals such as JSTAR, IJRS and PIER}
    {I appreciate the Examiner's vote of confidence. Portions of the work in this thesis have been written up as academic papers and submitted for peer-review.}

\replyToComment
    {Define terms heteroskedastic and homoskedastic in the context of SAR imagery.}
    {Heteroskedastic and homoskedastic are terms defined in a statistical context to respectively denote the fact that different sub-populations of given samples can have different or similar variabilities. In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or similar sample variance.}  %**IVM added the word 'sample'

@@

\replyToComment
    {Add references to the following statement: ``most of these data processing techniques are traditionally designed for additive and homoskedastic data.''}
    {Reference added: \cite{Dutch_LNCS_2004}.}

@@

\replyToComment
    {It would be easier to read and refer if all the Equations are labelled accordingly.}
    {All equations in the thesis have been updated with labels. Originally I had used labels only for equations which were important or were referred to later.}

@@

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
ToC & - & missing page numbers & Rectified \\
1 & 13 & single SAR channel & single-channel SAR \\ 
3 & 12 & Similarly speaking, & Similarly, \\
3 & 19 & criteria & criterion \\ 
4 & 14 & MMSE criteria & MMSE criterion \\
6 & 9 & Last but certainly not least, & Thirdly, \\ 
6 & 9 & such a framework allow & such a framework allows \\
9 & 7 & multidimensional & Multi-dimensional \\
10 & 12 & The model os & The model is \\
11 & 28 & chapter 5 & Chapter 5 \\
12 & 6 & chapter 6 & Chapter 6 \\
22 & 15 & RadarSat & RadarSat-2 \\
24 & 14 & SVM & SVM (Support Vector Machine) \\
35 & 6-7 & Rician distribution [48]... & Rician distribution [48]. \\
35 & 11 & back scattering & backscattering \\
36 & 10 & literatured & literature \\   %**IVM: Hai, please change the thesis to "literature" instead of "literatures"
37 & -2 & Proposed bu & proposed by \\
39 & 4 & dependence & dependency \\
44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence has been rephrased \\
46 & 4 & most known common & most commonly known \\
56 & 6 & POLSAR And & POLSAR. And \\
65 &5,7 & an homogeneous area & a homogeneous area \\
77 & 3 & the objective then is & the objective is \\
77 & 5,6 & it has already been proven & it has already been proven [?] \\
87 & -1 & Fig 5.6a & Fig 5.6. \\
89 & - & Figure 5.6 - subtitle (a) & (a) is removed \\
91 & - & Figure 5.8: Legends are too small to read & They have been enlarged \\
95 & - & Figure 5.12 & Use the same scale for  y axis (i.e MSE 0:1) across all the plots \\
103 & 22 & related to the ENL index. over & related to the ENL index over \\
104 & 13 & Equation 5.3.2.1 & The number is corrected to (?) \\  %**IVM: something missing here??
109 & 8 & Figs. 5.21c and 5.21d allows & Fig 5.21(a) and Fig 5.21(d) allow \\
112 & 13 & these smaller requirements & these requirements \\
132 & 9 & evaluation criteria & evaluation criterion
\end{longtable}    
\rowcolors{1}{white}{}

@@

In general, I wish to express my appreciation towards Examiner No. 2 for his careful, detailed and concise review.
%**IVM: I would skip this-> I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
I also feel encouraged by the Examiner's suggestion to extract out portions of this thesis as scientific papers for peer review, which has also been taken up and acted upon.
